---
title: "hw06-aidanh14"
author: "Aidan Hughes"
date: "November 7, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

Taken from the [homework HTML file](http://stat545.com/Classroom/assignments/hw05/hw05.html), here are the two topics I chose to complete for this assignment:

- Write one (or more) functions that do something useful to pieces of the Gapminder or Singer data.

- Create a nested data frame and map a function over the list column holding the nested data. Use list extraction or other functions to pull interesting information out of these results and work your way back to a simple data frame you can visualize and explore.

Before getting started, let load the necessary packages.

```{r packages}
suppressPackageStartupMessages(library("gapminder"))
suppressPackageStartupMessages(library("tidyverse"))
```

```{r}
cont_nests <- gapminder %>%
  group_by(continent) %>%
  nest()

europe_gap <- cont_nests %>%
  filter(continent == "Africa") %>%
  select(-continent) %>%
  unnest()

some_countries <- europe_gap$country %>%
  unique() %>% 
  {
    rand_nums <- sample(1:length(.), size=10)
    
    .[rand_nums] }

some_countries

europe_gap %>%
  group_by(country) %>%
  filter(country %in% some_countries) %>%
  ggplot(aes(x = pop, y = lifeExp)) +
  geom_point(aes(pop, lifeExp, colour = country)) +
  geom_smooth(aes(pop, lifeExp, colour = country), method = "lm", se = FALSE) +
  scale_x_log10()

```


```{r}
gap_linreg <- function (continent_df) {
  
}
```

